---
title: 'Week 4 Peer Assessmenr: Shiny Application and Reproducible Pitch'
author: "Max"
date: "10/09/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction 

This is an assessment from the Coursera data science course (Developing data products) in week 4. This presentation will introduce you about my Shiny application deployed on Rstudio's sever.

Here's the link to the shiny application: 
<https://doublefaces.shinyapps.io/Developing_data_products_week4_Shiny_App/>.

This is the link to the Github repository of the ui & sever.R: 
<https://github.com/Doublefacez/Developing-data-products-week-4-Peer-assessment>


## Data info
In this Shiny application, the mtcars data set was used.
This application uses different variables to plot against the mpg (Miles per Gallon) variable, also draws a simple regression line of (hp ~ mpg).

```{r head, cache=TRUE, echo=TRUE}
head(mtcars)
```
## Ui.R code

```{r ui, cache=TRUE, echo=TRUE, message=FALSE, results=FALSE}
library(shiny)

shinyUI(fluidPage(
    titlePanel("Cars Dataset - Miles per Gallon"),
  
  sidebarPanel(selectInput("var", "Variable:", 
                        c("Cylinders" = "cyl", "Transmission type" = "am",
                          "Gears" = "gear")),
            checkboxInput("model", "Show a simple regression model of hp vs mpg", 
                          value = FALSE),
                        submitButton("Sure! It seems cool")
        ),
  mainPanel(
            h3(textOutput("title")),
            plotOutput("plot1"),
            plotOutput("plot2")
  )
))
```


## Sever.R code

```{r sever, echo=TRUE}
library(shiny)
library(ggplot2)

data <- mtcars
data$am <- factor(data$am, labels = c("Auto", "Manual"))

shinyServer(function(input, output) {
    fig_title <- reactive({
        paste("mpg vs ", input$var)
    })
    output$title <- renderText({
        fig_title()
    })
    output$plot1 <- renderPlot({
        if(input$var == "cyl"){
            plot(mtcars$cyl, mtcars$mpg, main = "Plot of mpg vs cyl",
                 xlab = "Cylinders", ylab = "Miles Per Gallon (mpg)")
        }
        if(input$var == "am"){
        
            boxplot(mtcars$mpg, mtcars$am, names = c("Auto", "Manual"),
                    main = " Boxplot of mpg of each transmission type ")
        }
        if(input$var == "gear"){
            plot(mtcars$gear, mtcars$mpg,
                    main = " Plot of mpg of each gear", xlim = c(3, 5))
        }

    })
    output$plot2 <- renderPlot({
        if(input$model){
            model1 <- lm(hp~mpg, data = mtcars)
           
                plot(mtcars$mpg, mtcars$hp, xlab = "Miles per Gallon",
                     ylab = "Horsepower", bty = "n", pch = 16,
                     xlim = c(10,35), ylim = c(50, 350))
                abline(model1, col = "red", lwd = 2)
        }
        })
})

```



